Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
setwd('~/Documents/GitHub/DataAnalystNanodegree/R_test/EDA_Course_Materials/lesson3')
df <- read.delim('pseudo_facebook.tsv')
ggplot(aes(x = age, y = friend_count),
       data = subset(df, !is.na(gender))) + 
  geom_line(aes(color=gender), stat = 'summary', fun.y=median)

library(dplyr)
df.fc_by_age_gender <- subset(df, !is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
    median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = median_friend_count),
       data = df.fc_by_age_gender) +
  geom_line(aes(color=gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)

df.fc_by_age_gender.wide <- dcast(df.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')

#another way

install.packages('tidyr')
library(dplyr)
library(tidyr)
df.fc_by_age_gender.wide2 <-     subset(df.fc_by_age_gender[c('age', 'gender', 'median_friend_count')],!is.na(gender)) %>% 
    spread(gender, median_friend_count) %>% 
    mutate(ratio = female / male) 
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
library(ggplot2)
p = ggplot(aes(x=age,y=ratio), data=df.fc_by_age_gender.wide2) +
  geom_line() +
  geom_hline(yintercept =1, color = 'red', linetype=2)
print(p)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
df$year_joined <- floor(2014-df$tenure/365)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
df$year_joined.bucket <- cut(df$year_joined, breaks = c(2004,2009,2011,2012,2014))

df$prop_initiated <- ifelse(df$friend_count>0, df$friendships_initiated/df$friend_count, 0)

ggplot(data=df, aes(x=tenure,y=prop_initiated)) +
  geom_line(aes(color=year_joined.bucket), stat='summary', fun.y=median) +
  geom_smooth()
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(df$year_joined.bucket, useNA='ifany')

ggplot(data=subset(df, !is.na(gender)), aes(x=age, y=friend_count)) + 
  geom_line(aes(color=gender), stat = 'summary', fun.y=median)

ggplot(data=subset(df, !is.na(year_joined.bucket)), aes(x=age, y=friend_count)) +
  geom_line(aes(color=year_joined.bucket), stat = 'summary', fun.y=median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(data=subset(df, !is.na(year_joined.bucket)), aes(x=age, y=friend_count)) +
  geom_line(aes(color=year_joined.bucket), stat = 'summary', fun.y=mean) +
  geom_line(stat = 'summary', fun.y=mean, linetype=2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
ggplot(data = subset(df, tenure != 0), aes(x = age, y=friend_count/tenure)) +
  geom_line(stat='summary', fun.y=mean)

ggplot(data = subset(df, tenure != 0), aes(x=tenure, y=friend_count)) + geom_point()
 
with(subset(df, tenure != 0), mean(friend_count/tenure))
with(subset(df, tenure != 0), median(friend_count/tenure))
with(subset(df, tenure != 0), max(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(data = subset(df, tenure != 0), aes(x = tenure, y=friendships_initiated/tenure)) +
  geom_line(aes(color = year_joined.bucket),stat='summary', fun.y=mean) +
  geom_smooth(aes(color = year_joined.bucket), linetype=2)

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(df, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
setwd('~/Documents/GitHub/DataAnalystNanodegree/R_test/EDA_Course_Materials/lesson5')
yo <- read.csv('yogurt.csv')
str(yo)

yo$id <- factor(yo$id)
str(yo)

ggplot(data=yo, aes(price)) + 
  geom_histogram(binwidth = 10)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
unique(yo$price)
length(unique(yo$price))
table(yo$price)

yo$all.purchases <- yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry
  
yo <- transform(yo, all.purchases2 = yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(data = yo, aes(all.purchases)) +
  geom_histogram(binwidth=1)

ggplot(data = yo, aes(x=time, y=price)) + geom_jitter(alpha = 1/20)
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4239)
sample.ids <- sample(levels(yo$id), 16)

ggplot(data=subset(yo, id %in% sample.ids),aes(x=time, y=price)) +
  facet_wrap( ~ id) +
  geom_line() +
  geom_point(aes(size=all.purchases), pch=1)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***


```{r} 
library(GGally)
set.seed(1836)
df_subset <- df[, c(2:15)]
names(df_subset)
#ggpairs(df_subset[sample.int(nrow(df_subset), 1000), ])
```

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

