Lesson 3
========================================================

***

### What to Do First?
Notes: Reading in Data

***

### Pseudo-Facebook User Data
Notes: It's not the real Facebook Data

```{r Pseudo-Facebook User Data}
setwd('~/Documents/GitHub/DataAnalystNanodegree/R_test/EDA_Course_Materials/lesson3')
df <- read.delim('pseudo_facebook.tsv')
```

***

### Histogram of Users' Birthdays
Notes:theme_set() can change the theme

```{r Histogram of Users\' Birthdays}
library(ggplot2)
qplot(data = df, x = dob_day)
```

***

#### What are some things that you notice about this histogram?
Response: There are much more people who's birthday is in the first date of a month than other days

***

### Moira's Investigation
Notes: Whether people's perception of their audience on Facebook matches up to the reality 

***

### Estimating Your Audience Size
Notes: 

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response: Hello World!

#### How many of your friends do you think saw that post?
Response: 20

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response: 2%

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(data = df, x = dob_day) +
  scale_x_discrete(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)

```

#### Let's take another look at our plot. What stands out to you here?
Response: Most of the people's birthday is at January first. The reason for this result maybe because it's the default setting of Facebook and most of people didn't change it.

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira's outlier?
Response: bad data about an extreme case

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(data = df, x=friend_count)
```

#### How is this plot similar to Moira's first plot?
Response: There are people who have too many friends

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(data = df, x=friend_count, xlim=c(0, 1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes: qplot(x = friend_count, data = df, binwidth = 10)

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = df, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(df, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(df$gender)
by(df$friend_count, df$gender, summary)
```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: it's more resistance to change from those outliers.

***

### Tenure
Notes:

```{r Tenure}
qplot(data=df, x=tenure, binwidth=30, color = I('black'), fill=I('#099DD9'))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(data=df, x=tenure/365, breaks=seq(0,7,0.25), color = I('black'), fill=I('#099DD9'))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(data=df, x=tenure/365, breaks=seq(0,7,0.25), xlab="Number of years using Facebook", ylab="Number of users in sample", color = I('black'), fill=I('#099DD9'))
```

***

### User Ages
Notes:

```{r User Ages}
qplot(data=df, x=age, xlab="Age of user", binwidth=10, ylab="Number of users in sample", color = I('black'), fill=I('#099DD9'))
```

#### What do you notice?
Response:
No users' age is under 10 (actually, it's 13)
***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***
```{r Transforming Data}
summary(log10(df$friend_count+1))
summary(sqrt(df$friend_count))

library(gridExtra)
g1 <- qplot(data=df, x=friend_count)
g2 <- qplot(data=df, x=log10(friend_count+1))
g3 <- qplot(data=df, x=sqrt(friend_count))
g4 <- g1+scale_x_log10()
grid.arrange( g1, g2, g3, g4, nrow=4)
```

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
library(gridExtra)
g1 <- qplot(data=df, x=log10(friend_count+1))
g2 <- qplot(data=df, x=friend_count) + scale_x_log10()
gg <- ggplot(data=df, aes(x=friend_count)) + geom_histogram()  + scale_x_log10()
grid.arrange( g1, g2, gg, nrow=3)
```

***


### Frequency Polygons

```{r Frequency Polygons}
g1 = qplot(data=subset(df, !is.na(gender)), x=friend_count, y=..count../sum(..count..), geom = 'freqpoly', color=gender, breaks=seq(0,3000,50), xlab='Friend Count', ylab='Proportion of Users with that friend count') 

g2 = qplot(data=subset(df, !is.na(gender)), x=friend_count, y=..count../sum(..count..), geom = 'freqpoly', color=gender) +
  scale_x_log10()

grid.arrange( g1, g2, nrow=2)
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
qplot(data=subset(df, !is.na(gender)), x=www_likes, y=..count../sum(..count..), geom = 'freqpoly', color=gender, breaks=seq(100,1000,50), xlab='Friend Count', ylab='Proportion of Users with that friend count') 

by(df$www_likes, df$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(data=subset(df, !is.na(gender)), 
      x=gender, y=friend_count, 
      geom='boxplot')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(data=subset(df, !is.na(gender) & friend_count<1000), 
      x=gender, y=friend_count, 
      geom='boxplot')
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
qplot(data=subset(df, !is.na(gender)), 
      x=gender, y=friend_count, 
      geom='boxplot') +
  coord_cartesian(ylim=c(0,300))
```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
qplot(data=subset(df, !is.na(gender)), 
      x=gender, y=friendships_initiated, 
      geom='boxplot') +
  coord_cartesian(ylim=c(0,150))

by(df$friendships_initiated, df$gender, summary)
```

Response: All the 3rd Quart, Mean, Median and 1st Quart number of friendships_initiated in female is more than  the number in male

***

### Getting Logical
Notes:

```{r Getting Logical}
df$mobile_check_in <- NA
df$mobile_check_in <- ifelse(df$mobile_likes > 0, 1, 0)

mci <- table(df$mobile_check_in)
mci[2] / (mci[1]+mci[2])

sum(df$mobile_check_in == 1)/length(df$mobile_check_in)
```

Response: 65%
***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!