Lesson 4
========================================================

***

```{r Pseudo-Facebook User Data}
setwd('~/Documents/GitHub/DataAnalystNanodegree/R_test/EDA_Course_Materials/lesson3')
df <- read.delim('pseudo_facebook.tsv')
```

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
qplot(data = df, x = age, y = friend_count)
```

***

#### What are some things that you notice right away?
Response:
People who's age is under 30 have more friends
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
qplot(data = df, x = age, y = friend_count)
ggplot(aes(x=age, y=friend_count), data=df) + xlim(13,90) + geom_point()
summary(df$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age, y=friend_count), data=df) + 
  geom_point(alpha = 1/20) + 
  xlim(13,90)

ggplot(aes(x=age, y=friend_count), data=df) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13,90)
```

#### What do you notice in the plot?
Response:
People who's age is under 30 have more friends
***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x=age, y=sqrt(friend_count)), data=df) + 
  geom_point(alpha = 1/20) + 
  xlim(13,90)

ggplot(aes(x=age, y=friend_count), data=df) + 
  geom_point(alpha = 1/20) + 
  xlim(13,90) +
  scale_y_sqrt()
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x=age, y=friend_count), data=df) + 
  geom_point(alpha = 1/20, position = position_jitter(h=0)) + 
  xlim(13,90) +
  coord_trans(y = 'sqrt')
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x=age, y=friendships_initiated), data=df) + 
  geom_point(alpha = 1/20, position = position_jitter(h=0)) + 
  xlim(13,90)
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)
age_groups <- group_by(df, age)
print(age_groups)
df.fc_by_age <- summarise(age_groups, 
         friend_count_mean = mean(friend_count),
         friend_count_median = median(friend_count),
         n = n())
df.fc_by_age <- arrange(df.fc_by_age, age)
```

Create your plot!

```{r Conditional Means Plot}
df.fc_by_age <- df %.%
  group_by(age) %.%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n=n()) %.%
  arrange(age)

head(df.fc_by_age)
ggplot(data = df.fc_by_age, aes(x=age, y=friend_count_mean)) + geom_line()

ggplot(data = df.fc_by_age, aes(x=age, y=friend_count_median)) + geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x=age, y=friend_count), data=df) + 
  geom_point(alpha = 1/20, position = position_jitter(h=0), color='orange') + 
  xlim(13,90) +
  coord_trans(y = 'sqrt') +
  geom_line(stat='summary', fun.y=mean) +
  geom_line(stat='summary', fun.y=quantile, probs=0.25, linetype=2, color='blue') +
  geom_line(stat='summary', fun.y=quantile, probs=0.75, linetype=2, color='red')

by(df$friend_count, df$age, summary)
```

#### What are some of your observations of the plot?
Response:
90% of people have friends below 1000
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor(df$age, df$friend_count, method='pearson')
with(df, cor.test(age, friend_count, method='pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(df, age<=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

